Dirac neutrino mass generation from Majorana messenger

### 2019-09-15 draft.tex
Updates from Overleaf

\section{Beyond the minimal model: cosmological constraints}
\label{sec:CosmoConstraints}
\ref{eq:LagY}
It turns that the $Z'$ portal also allows to probe the model through modifications on the cosmological history of the Universe, namely, via additional contributions to the effective number of relativistic degrees of freedom $N_{\text{eff}}$. These contributions, which arise from the presence of the new light states $\nu_R$'s, are expected to be sizeable due to the large $X$ charges of $\nu_R$'s in our model . However, since they do not couple directly to any SM particles, we can simply assume that their interaction with the extra gauge boson and scalars are sufficiently suppressed that they  decouple early enough from the thermal bath.

>>>>

\section{Beyond the minimal model: cosmological constraints}
\label{sec:CosmoConstraints}
\ref{eq:LagY}
It turns that the $Z'$ portal also allows to probe the model through modifications on the cosmological history of the Universe, namely, via additional contributions to the effective number of relativistic degrees of freedom $N_{\text{eff}}$. These contributions, which arise from the presence of the new light states $\nu_R$'s, are expected to be sizeable due to the large $X$ charges of $\nu_R$'s.  However, since they do not couple directly to any SM particles, we can simply assume that their interaction with the extra gauge boson and scalars are sufficiently suppressed that they  decouple early enough from the thermal bath.
